%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SSR Data Scientist -- S\&OP Solutions} % Job title
    {Novix SA} % Organization
    {Cordoba, Argentina} % Location
    {Jun. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a Master Production Schedule solution for multinational food company. - Python}
      \item {Developed a Master Production Schedule solution for multinational food company. - Python}
      \item {Constructed a production optimization prototype for multinational food company. - CVXPY}
      \item {Implemented an integration between SAP and an Analytic framework for multinational food company - Python}
      \item {Participated in production optimization solution - Pulp}
      \item {Developed a Load pipeline from Azure Gen2 Data lake for a pharmaceutical company - Python}      
      \item {Designed ab amortization schema for a bank - Python}      
      \item {Provided technical support to the team (15 people) - Python}
      \end{cvitems}
    }	
	
%---------------------------------------------------------
  \cventry
    {External Consultant} % Job title
    {IDB Invest} % Organization
    {Offices NY - Remote} % Location
    {Sept. 2020 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a tool for generating financial reports. - VBA.}
      \item {Built an ETL process for financial metrics supervision. - Python}
      \item {Computed metrics for loan scoring.- Python}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {External Consultant} % Job title
	{Secretary of Applied Studies, Ministry of Government} % Organization
    {Cordoba, Argentina} % Location
    {Jul. 2020 - Present} % Date(s)
    {
     \begin{cvitems} % Description(s) of tasks/responsibilities
     \item {Performed ad-hoc analysis on dimension tables. - Python.}
     \item {Automated ETL process for subsidy scheme analysis. - Oracle DB and Python}
     \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Associate Research Analyst} % Job title
    {Mediterranea Foundation} % Organization
    {Cordoba, Argentina} % Location
    {Sep. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Estimated the deficit of Latin American pension systems using Household National Surveys - Calculations performed using the Tidyverse framework.}
      \item {Developed metrics for weekly articles on www.ieral.org.}
      \item {Conducted predictions of coronavirus cases in Cordoba Province using the SEIR Model.}
      \item {Automated data entry using Pdftools.}
      \item {Performed static scraping using Rvest.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Adjunct Assistant Professor of Mathematical Statistics} % Job title
    {Faculty of Economic Sciences National University of Cordoba} % Organization
    {Cordoba, Argentina} % Location
    {Mar. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Provided weekly support lessons on various topics including probability computation, computation of density function properties, density function derivation using the Jacobian method, computation of median, expected values, variance, and higher-order moments, maximum likelihood estimation, and asymptotic theory.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Autonomous} % Organization
    {Cordoba, Argentina} % Location
	{Jun. 2018 - Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
   	\item {Conducted personalized explanatory analysis for a Rugby Club and an Oncologic Foundation using the Tidyverse framework.}
	\item {Developed a Shiny app for a Law Firm.}
	\item {Prepared datasets for a discrete choice model analysis.}
      \end{cvitems}
    }

    
%---------------------------------------------------------
  \cventry
    {Intern Analyst} % Job title
    {Debt Office, Ministry of Finance} % Organization
    {Cordoba, Argentina} % Location
    {Sep. 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Constructed and maintained indexes for monitoring subnational debt instruments.}
      \item {Conducted on-demand analysis, including interstate revenue collection comparisons, debt stock time-series analysis, interest rates comparisons, and WACC calculations using MS Excel.}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
\end{cventries}
